Future challenges for Research Software Engineering

### 2025-05-17 future_challenges_for_RSEng.tex
change tense

\begin{story}{The Definition of RSEs}{defrse}
Kim and Kay chuckled as they looked at their original job descriptions from 2020—"build tools for scientists, manage data, write reusable code."
Now, their roles were unrecognizable: half AI whisperer, half research ethicist, and part-time diplomat between synthetic and human collaborators.
They managed not just software, but the personalities of autonomous lab agents and negotiated data-sharing agreements with international AI consortiums.
Despite the tech upheaval, their deep knowledge of scientific workflows and the messy, human way science actually gets done remained indispensable.
When labs faltered under algorithmic bias or unclear model provenance, it was Kim and Kay who translated the chaos back into meaning.
They understood that science didn’t move in straight lines, and that trust—between collaborators, institutions, and even machines—had to be built, not coded.
Their titles had changed, but their role as bridges between logic and life remained the same.
In a future of shifting code and constant reinvention, it was their understanding of people that never went out of date.

>>>>

\begin{story}{The Definition of RSEs}{defrse}
Kim and Kay chuckled when they looked at their original job descriptions from 2020: "build tools for scientists, manage data, write reusable code."
Now, their roles are unrecognizable: half AI whisperer, half research ethicist, and part-time diplomat negotiating between synthetic and human collaborators.
They now not only manage software, but also the personalities of autonomous lab agents and negotiate data-sharing agreements with international AI consortia.
Despite the tech upheaval, their deep knowledge of scientific workflows and the messy, human way science actually gets done remains indispensable.
When labs faltered under algorithmic bias or unclear model provenance, it was Kim and Kay who transformed the chaos back into meaningful order.
They understand that science does not move in straight lines, and that trust between collaborators, institutions, and even machines has to be built, not coded.
Their job titles have changed, but their role as bridges between logic and life remains the same.
In a future of shifting code and constant reinvention, it is their understanding of people that never went out of date.
